A survey of HTTP caching options on the open Semantic Web

### 2015-01-16 sanity/paper1.tex
Now start trimming
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@993 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{abstract}
Scalability of the data access architecture in the Semantic Web is
dependent on the establishment of caching mechanisms to take the load
off of servers.  Unfortunately, there is a chicken and egg problem
here: research, implementation, and evaluation of caching
infrastructure is uninteresting as long as data providers do not
publish relevant metadata.  And publishing metadata is useless as long
as there is no infrastructure that uses it.

>>>>

\begin{abstract}
Scalability of the data access architecture in the Semantic Web is
dependent on the establishment of caching mechanisms to take the load
off of servers.  Unfortunately, there is a chicken and egg problem
here: Research, implementation, and evaluation of caching
infrastructure is uninteresting as long as data providers do not
publish relevant metadata.  And publishing metadata is useless as long
as there is no infrastructure that uses it.
